Weather Data Integration and Assimilation System\\

### 2020-02-10 method/sec_3-microservice.tex

<explain how each one is used while designing the WDIAS architecture>

\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for server requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}

>>>>

<explain how each one is used while designing the WDIAS architecture>
In the figures of \ref{fi:wdias_micro_on_demand} and \ref{fi:wdias_micro_async} each circle represent a microservice, and those are implemented as containerized applications.
\begin{figure}[htp]
    \centering
    \includegraphics[width=1\textwidth]{method/microservice/microservice_architecture-handle_on_demand-v3.jpg}
    \caption{\acrshort{wdias} architecture for server requests on demand}
    \label{fi:wdias_micro_on_demand}
\end{figure}
